Avoiding tipping points in fisheries management through Gaussian Process Dynamic Programming

### 2014-07-01 manuscripts/manuscript.Rmd
as submitted

---
layout: 12pt,review
linenumbers: true
title: "Avoiding tipping points in fisheries management: A Bayesian Non-Parametric approach"
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig(at)gmail.com
    footnote: Corresponding author
  - name: Marc Mangel
    affiliation: cstar
  - name: Stephan Munch
    affiliation: noaa
address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research, 
      Department of Applied Math and Statistics, 
      University of California, Mail Stop SOE-2,
      Santa Cruz, CA 95064, USA
  - code: marc
    address: |
      Center for Stock Assessment Research, Department of Applied Math
      and Statistics, University of California,
      Mail Stop SOE-2, Santa Cruz, CA 95064, USA and Department of
      Biology, University of Bergen, Bergen, Norway 9020
  - code: noaa
    address: | 
      Southwest Fisheries Science Center, 
      National Oceanic and Atmospheric Administration, 
      110 Shaffer Road, Santa Cruz, CA 95060, USA

>>>>

---
layout: 12pt,review
linenumbers: true
title: "Avoiding tipping points in fisheries management through Gaussian Process Dynamic Programming"
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig(at)gmail.com
    footnote: Corresponding author
  - name: Marc Mangel
    affiliation: cstar
  - name: Stephan Munch
    affiliation: noaa
address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research, 
      Department of Applied Math and Statistics, 
      University of California, Mail Stop SOE-2,
      Santa Cruz, CA 95064, USA
  - code: marc
    address: |
      Center for Stock Assessment Research, Department of Applied Math
      and Statistics, University of California,
      Mail Stop SOE-2, Santa Cruz, CA 95064, USA and Department of
      Biology, University of Bergen, Bergen, Norway 9020
  - code: noaa
    address: | 
      Southwest Fisheries Science Center, 
      National Oceanic and Atmospheric Administration, 
      110 Shaffer Road, Santa Cruz, CA 95060, USA
